A review on Generative Learning in Computer Vision

### 2020-05-07 paper.tex
added acgan

\subsubsection{Auxiliary Classifier GAN}

>>>>

\subsubsection{Auxiliary Classifier GAN}
Auxiliary classifier GAN (ACGAN), proposed by Odena et al in 2017 \cite{b7}, is able to generate high-resolution images using a technique called label conditioning. At that time, the experiment resulted in images of 128 x 128 resolution images. They also were able to identify the collapsing behavior of a GAN. The model the presented is a conditional model which was able to took a lot of lables/classes as supplementary input. They were able to create highly different sample spaces at a time. Unlike CGAN, the discriminator in this case learnt the supplementary information on its own, this technique is referred as reconstruction loss.
